\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-08-31 Paper/Paper.tex
rename ODADS in code to MAAM; change table headers to abbr.

	\begin{table}[htbp]
		\centering
		\caption{OCT Test}
		\label{tb:OCT_test}
		\pgfplotstabletypeset[
		multicolumn names,
		col sep=comma,
		columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
		columns/Abnormity/.style={string type, column name=Abnormities},
		columns/Precision/.style={string type, column name=Precision},
		columns/Sensitivity/.style={string type, column name=Sensitivity},
		columns/Specificity/.style={string type, column name=Specificity},
		columns/FOne/.style={string type, column name={F1 Score}},
		columns/AUC/.style={string type, column name=AUC},
		every head row/.style={before row=\toprule, after row=\midrule},
		every last row/.style={ after row=\bottomrule}
		]{Tables/abnormity_o_test.csv}
	\end{table}

	\begin{table}[htbp]
		\centering
		\caption{Fundus Test}
		\label{tb:Fundus_test}
		\pgfplotstabletypeset[
		multicolumn names,
		col sep=comma,
		columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
		columns/Abnormity/.style={string type, column name=Abnormities},
		columns/Precision/.style={string type, column name=Precision},
		columns/Sensitivity/.style={string type, column name=Sensitivity},
		columns/Specificity/.style={string type, column name=Specificity},
		columns/FOne/.style={string type, column name={F1 Score}},
		columns/AUC/.style={string type, column name=AUC},
		every head row/.style={before row=\toprule, after row=\midrule},
		every last row/.style={after row=\bottomrule}
		]{Tables/abnormity_f_test.csv}
	\end{table}

@@

	\begin{table}[htbp]
		\centering
		\caption{Diagnosis Test}
		\label{tb:diagnosis_test}
		\pgfplotstabletypeset[
		multicolumn names,
		col sep=comma,
		columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
		columns/Abnormity/.style={string type, column name=Abnormities},
		columns/Precision/.style={string type, column name=Precision},
		columns/Sensitivity/.style={string type, column name=Sensitivity},
		columns/Specificity/.style={string type, column name=Specificity},
		columns/FOne/.style={string type, column name={F1 Score}},
		columns/AUC/.style={string type, column name=AUC},
		every head row/.style={before row=\toprule, after row=\midrule},
		every last row/.style={ after row=\bottomrule}
		]{Tables/diagnosis2.csv}
	\end{table}

>>>>

			\begin{table}[htbp]
				\centering
				\fontsize{9}{12}\selectfont{
				\caption{OCT Test}
				\label{tb:OCT_test}
				\pgfplotstabletypeset[
				multicolumn names,
				col sep=comma,
				columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
				columns/Abnormity/.style={string type, column name=Abnormities},
				columns/Precision/.style={string type, column name=Precision},
				columns/Sensitivity/.style={string type, column name=Sensitivity},
				columns/Specificity/.style={string type, column name=Specificity},
				columns/FOne/.style={string type, column name={F1 Score}},
				columns/AUC/.style={string type, column name=AUC},
				every head row/.style={before row=\toprule, after row=\midrule},
				every last row/.style={ after row=\bottomrule}
				]{Tables/abnormity_o_test.csv}}
			\end{table}

			\begin{table}[htbp]
				\centering
				\fontsize{9}{12}\selectfont{
				\caption{Fundus Test}
				\label{tb:Fundus_test}
				\pgfplotstabletypeset[
				multicolumn names,
				col sep=comma,
				columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
				columns/Abnormity/.style={string type, column name=Abnormities},
				columns/Precision/.style={string type, column name=Precision},
				columns/Sensitivity/.style={string type, column name=Sensitivity},
				columns/Specificity/.style={string type, column name=Specificity},
				columns/FOne/.style={string type, column name={F1 Score}},
				columns/AUC/.style={string type, column name=AUC},
				every head row/.style={before row=\toprule, after row=\midrule},
				every last row/.style={after row=\bottomrule}
				]{Tables/abnormity_f_test.csv}}
			\end{table}

@@

	\begin{table}[htbp]
		\centering
		\fontsize{9}{12}\selectfont{
		\caption{Diagnosis Test}
		\label{tb:diagnosis_test}
		\pgfplotstabletypeset[
		multicolumn names,
		col sep=comma,
		columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
		columns/Abnormity/.style={string type, column name=Abnormities},
		columns/Precision/.style={string type, column name=Precision},
		columns/Sensitivity/.style={string type, column name=Sensitivity},
		columns/Specificity/.style={string type, column name=Specificity},
		columns/FOne/.style={string type, column name={F1 Score}},
		columns/AUC/.style={string type, column name=AUC},
		every head row/.style={before row=\toprule, after row=\midrule},
		every last row/.style={ after row=\bottomrule}
		]{Tables/diagnosis2.csv}}
	\end{table}
